\section{Future Work}
Because of the benefits of the NeuroML model specification, data fitted models should be downloadable in a NeuroML format. NeuroML is simulator agnostic, descriptions of the optimized models will be more shareable, if they are not pinned down to implementations used here. Neuron modellers likely already have their favorite simulator framework. Optimized NeuroML can can be executed on any mainstream simulator. 

The next most obvious improvements to the optimizer is simple. In this work I reveal a serious problem caused by insufficiently accurate rheobase calculations where small sources of rounding error  propagate into some other measurements. % I may not have labored the case %P where they produce large detectable oscillations. 
Despite there being negative consequences of this error for the signal sources that guide optimization, there is still a mandate for models with different preferred currents to participate in testing. Preferred current searches are easily separable from Genetic Algorithms, meaning that a preferred current search can occur in an isolated part of a different algorithm where it will not act as the basis for electrical measurements. Over the course of a genetic algorithms search a fixed current can be applied to all models, allowing electrical measurements to be grounded to a stable value. Genetic algorithms can easily be nested inside each other, its easy to conceive of a situation, where an inner GA evaluates model fitness according to fixed currents, and an outer GA changes the fixed current that is used on each inner GA batch. The result of such a process should be a collection of optimized cells, that where obtained according to a different fixed current injection strength. %If one optimized model is clearly better, then two things about the model are revealed. What is the cell models preferred current, and what how well did it fit the tests? This scheme is also different in that it treats current injection strength as a model parameter, and not a emergent feature of the model.

%cause of this finite precision error, 
%When model parameters are inserted into NeuroML cell model definitions, NeuroML encoded models become operational. These NeuroML encodings will if possible be uploaded into NeuroML-DB, where they will be more readily find-able by the neuron modelling community
% Such files can be used as network components, and they confidently utilized and exchanged, as such files represent a higher degree of rigor. Since there are two classes of model fits, some models are better suited fitted to network modelling and others are better suited to single cell modelling, this is because, by fitting cell models to FI curves, a lot of other realistic electrical behavior that is incompatible with the FI fit diminishes.

At least for the Izhikevich, model links to the reference models, can also be provided.

The are several valid instances when the complete three dimensional form of a neuron (and the 3D form of a network) is an integral part of a brain simulation, such as in the Blue Brain somato-sensory cortex model \cite{markram2006blue} and the Allen Institute \emph{V1} model \cite{billeh2020systematic}, The Allen Institute \emph{V1} simulation was improved by encasing a "core" of biophysically accurate models inside a "shell" of simple fast and reduced GLIF models. Results from this work suggests that pre-existing large scale brain simulations might be further improved by including a shell of AdEx or Izhikevich models.% The literature states only GLIF models, I am not proposing what they should do, only what I have read about.

%Izhikevich, GLIF, or Adaptive Exponential Integrate and Fire models.\\ 

\subsubsection{Merits of Extending Biophysical Accurate Simulations by Including Reduced Models}
Almost all cortical neurons experience ``tonic" synaptic input and these tonic inputs originate from neurons from a different part of the brain. One strategy for handling missing inputs to the region of interest, is to simply model spike trains for each input synapse. This approach to modelling synapses is called a Point Process, or a spike train surrogate. Modern programming languages have tools that can make the synthesis of statistically similar spike trains easy and convenient. One big problem with this approach is that such surrogate spike trains are impervious to Local Field Potential (LFP) analysis, as point processes fail to model current flow in the soma and dendrites. Because synapse activation is predicted using stochastic models, the mechanistic reasons that lead to firing are opaque in the point process model, likely there will be no physical sequence of cause and effect steps to explain synapse firing. Although point process modelling sounds potentially simple, point process models can in fact be very elaborate, and therefore they may be slow to execute. Reduced models by contrast, are potentially fast to evaluate, their mechanisms are transparent and have some phenomenological relationship to membrane physics. Reduced models can also produce somatic currents. Somatic currents may facilitate the imputation of dendritic current. Modelled somatic currents can therefore be read-out and measured in network models of Local Field Potential.
%assumes that post synaptic neurons are mainly influenced by the firing rate of inputs, if they pre-synaptic neurons are actually conveying important code words via exact interspike intervals, a statistical approach to modelling spike trains would not do.\\

%than generating only psuedo random timed inputs to synapses, 
In the case of the Allen Institute Model, if the region of interest V1 is a "core" of realistic neurons. That is a kernel of realistic neurons encased by a shell of less realistic neurons. Inputs to V1 also come from the outer encasement of neurons. It is therefore of interest if these external GLIF models can or should be substituted with optimized Izhikivich and AdEx models, in case substiting GLIF for Adex results in an overall more realistic network simulation. In that case, even the external shell of simulation could experience a marginal improvement in accuracy. In network models there are benefits of reduced models over the use of a point process or a spike train surrogate.\\

% benefits: interpretability, transparent function, has current so contributes to LFP

One of these benefits is that the firing of reduced neural models can be made to be causal, such that its spike times are not just what statistically matches missing models. Furthermore reduced models can still participate in networks, reduced models can become disconnected or participate in an dynamic assembly. Realistic levels of plasticity of the modelled network is more possible with included reduced models, than statistical surrogates of those models.

Furthermore Izhikevitch and AdExp models are commonly utilized in neuromorphic spiking neural networks in artificial intelligence and bio medical modelling contexts.

Encasing a core of complex models inside a shell of simplified models mitigates a harmful edge effect. The problem is that simulations concern sub divisions of brain tissue and without intervention the act of making a subdivision severe synaptic inputs. All published highly detailed simulations to date, have necessitated the simulation of severed volumes of tissue, and this creates another problem to manage.\\