
Multiple constraining factors effect the design of large scale cortical brain simulations, these are: simulation time, empirical validity, understand-ability and reproducibility. A class of digital neuronal models: "Reduced Neural models", are faster and easier to interpret than multicompartment conductance based models. Reduced models are one of multiple model types used in brain simulations, and they are often utilized as a buffer, for parts of simulations when poorer standards of model/experiment agreement are  tolerated. Large scale cortical brain simulations could be improved if higher standards of model/experiment agreement were satisfied in reduced neuronal models as well as in multi-compartment neurons, as this could bring about more accurate simulations for the same rapid simulation speed. Motivated by the promise of good speed and improved accuracy we used numerical simulations on reduced models inside a genetic algorithm data fitting framework. To explore the upper limit of model/experimental agreement, and thereby obtain experimental fits at the highest possible quality. Unsurprisingly Reduced neuronal models were not unlimited in their flexibility and fidelity. For the three types of reduced neuronal model we were able to obtain models that produced mostly biologically plausible measurements, for six or seven out of eight fitness criteria, however, consistently one or two in every eight measurement needed to be pushed past the range of plausability, in-order to produce an "all-round" empirically valid cell model. In contrast with existing approaches that have succeeded in fitting reduced neuronal models to the onset frequency and exact times of neuron firing, in this work we disregarded spike timing, and instead fitted models to transient electrical properties, and waveform shapes recorded from different neuronal membranes.\\
\\
%In order to investigate how well reduced models can reproduce experimental data we executed numerical simulations, and coupled the simulations with a genetic algorithm workflow. We used data sourced from neuroelectro.org, and 
\\ 
%Among alternative models such as Point-process spike chain surrogates, and  multi compartment conductance models, only reduced neuronal models are faster to execute, and easier to interpret. 

%Three subtypes of reduced neuronal models, represent a midway point, in terms of their ability to faithfully reproduce experimental findings.\\
\\

%combined it with a selection of differential equation solvers. custom written differential equation solvers for the Adaptive Exponential, Izhikevich, and simple conductance based models.\\
% Reduced models are a crucial component of many large scale brain simulations.
%in these fast to execute models. 
%We wanted to understand the limits of fitting reduced neural models to experimental electrophysiology measurements, and to use this knowledge to acquire the best possible fits between reduced neuron models and experimental electrical measurements.


%. in this class of models. \\
%\\

%We computed normalized Z-scores.

% * The methods were using a genetic algorithms to solve multiobjective optimization problem. Forward euler solvers


% Additionally reduced neuronal models simulate current flow, and thus are compatible with local field potential models. Although they are not spatially 


% Fulfil and understand the limits of reduced model fitting and agreeing to experiments. 

%as best as possible, fit reduced neural models to experimental measurements, and then to understand and describe limitations in models, that stop impede fitting and cause disagreement between models and experimental measurements.
%of the agreement between reduced neural models and experimental data reproduce experimentally observed neural measurements.
%Since This also involved exploring limitations in some types of neural data.
%* Euclidiating the limits of reduced models and the limits of data, that impede model fitting.
%* Euclidiating model measurement challenges (Rheobase as a soft constraint, threshold computations).
%to data. I
%METHODS 

% It is not novel to embed numerical model simulation inside genetic algorithms, but it is novel recompute rheobase at every sampled model parameter set, and thus to promote a diverse array of model types to the possibility of single spike waveform shape checking.


%Your research problem and objectives
%    Your methods
%    Your key results or arguments: python, numba, dask, dashboard, multiobjective optimisation, open source, reproducibility.
%    Your conclusion