\chapter{Discussion}
In this thesis I have described a number of methods that I developed and implemented to optimize reduced neuron models against experimental data collected from real neurons.
I then verified that this optimizer works in the sense of being able to recover ground truth models given only simulated data from those models.
I showed that successful optimization depends upon certain characteristics of the experimental data and the features extracted from it, and identified a flaw in the approach of optimizing against aggregated data from neural populations. 
I demonstrated that the optimizer does an adequate job at fitting reduced neuron models to real experimental data from single neurons, and that certain models (and cell types) are easier to optimize than others.
I showed that published models differ from the experimental data they ought to be explaining, on which features they differ most, and I show proto-typed analysis pathway that is capable of demonstrating if and when optimized models can better match experimental data, compared to other published models.
%and that it is possible to optimize these models to better match those experimental data.
Finally, I presented a tool to bring this optimization framework to the masses.

\emph{Efficient} optimization of reduced neuron models is shockingly non-trivial, although satisficing biologically plausible models is several degrees easier.
Below I provide a number of examples of optimization pitfalls which were not obvious at the start of my research, but which I discovered during my research, and which were on ongoing source of confusion, not just for me, but for my whole research team.
I believe that it is important to share these conceptual traps with my readership, including those who may wish to continue such optimization work.

\input{chapters/discussion/DISCUSSION_optimization_requirements}
\input{chapters/discussion/DISCUSSION_error_surfaces}
\input{chapters/discussion/DISCUSSION_conflicted_tests}
\input{chapters/discussion/DISCUSSION_significance_of_results}
\input{chapters/discussion/DISCUSSION_target_network_simulations}
\input{chapters/discussion/DISCUSSION_other}
\input{chapters/discussion/DISCUSSION_future_work}